Considering scale in multilayer animal social networks

### 2020-06-14 paper/manuscript.Rmd
add time defs

library(data.table)
DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
```

>>>>

library(data.table)
DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
timedefs <- fread('../data/supp-data/timecut-defs.csv')
```
